NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2020-02-10 Manuscript/manuscriptPGPE.tex
Add results from headgroup tilt by P. Buslaev to the manuscript from https://github.com/NMRLipids/NMRlipidsIVPEandPG/issues/9
Update PG, PE and PC mixtures data

@@

  \caption{List of MD simulations with PE and PG lipids mixed with PC.
  }\label{systemsMIX}
      lipid/counter-ions & force field for lipids / ions & NaCl (M) & CaCl$_2$\,(M) &  \footnote{Number of lipid molecules with largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$   & \footnote{Number of additional cations}N$_{\rm c}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns) & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns) &   \footnote{Reference for simulation files}files\\
      POPC                   & CHARMM36 \cite{??}        & 0.11      & 0  & 500     & 25000 & 48  &  310  & 500 & 100 & \cite{POPCcharmm150mMNaCl301K}  \\
      POPC:POPG (7:3)        & CHARMM36 \cite{??}        & 0.11      & 0  & 350     & ?     & ?   &  310  & 500 & 100 & \cite{POPC7POPG1charmm36NaCl}  \\
      POPC:POPG (1:1)/K$^+$  & CHARMM36 \cite{??}        &0          & 0  & 250:250 & 18158 & 0   &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG5050} \\ 
      POPC:POPG (1:1)        & CHARMM36 \cite{??}        &0          & 0.34 \todoi{Concentration calculated based in total amount of calcium ions. This may not be reasonable due to the lack of counterions.}  & 250:250 & 20798 & 128 &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG5050150mMCaCl} \\
      POPC:POPG (1:1)        & CHARMM36 \cite{??}        &0          & 1.36  \todoi{Concentration calculated based in total amount of calcium ions. This may not be reasonable due to the lack of counterions.} & 250:250 & 18114 & 445  &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG50501000mMCaCl} \\
      POPC:POPG (4:1)/K$^+$  & CHARMM36 \cite{??}        &0          & 0  & 400:100 & 18664 & 0  &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG4010} \\
      POPC:POPG (4:1)/K$^+$  & CHARMM36 \cite{??}        &0          & 1.0 \todoi{Concentration calculated based in total amount of calcium ions. This may not be reasonable due to the lack of counterions.} & 400:100 & 18647 & 419  &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG40101000mMCaCl} \\
      POPC             & CHARMM36 \cite{??}        &0          & 0  & 256 & 8704 & 0  &  300  & 300 & 250 & \cite{POPCcharmm300K} \\
      POPC:POPE (1:1)  & CHARMM36 \cite{??}        &0          & 0  & 128 & 8704 & 0  &  300  & 300 & 250 & \cite{POPC1POPE1charmm36} \\
      POPC                   & Slipid \cite{??}        & 0.11      & 0  & 500     & 25000 & 48  &  310  & 500 & 100 & \cite{POPCslipid150mMNaCl301K}  \\
      POPC:POPG (7:3)        & Slipid \cite{??}        & ?         & 0  & ?     & ?     & ?   &  310  & 500 & 100 & \cite{??} \todoi{Zenodo entry unclear.}  \\
      POPC             & Berger \cite{??} \todoi{This is probable not plain berger, correct force filed should be described.}  &0  & 0  & 256 & 10240 & 0  &  300  & 300 & 200 & \cite{POPCberger300K} \\
      POPC:POPE (1:1)  & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.} &0          & 0  & 128 & 11008 & 0  &  300  & 300 & 200 & \cite{POPC1POPE1berger} \\
      POPC:DOPE (1:1)  & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.}         &0          & 0  & 128 & 10240 & 0  &  300  & 300 & 200 & \cite{POPC1DOPE1berger} \\
      DOPC             & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.}         &0          & 0  & 256 & 11008 & 0  &  300  & 300 & 200 & \cite{DOPCberger300K} \\
      DOPC:DOPE (1:1)  & Berger \cite{??}   \todoi{This is probable not plain berger, correct force filed should be described.}        &0          & 0  & 128 & 11008 & 0  &  300  & 300 & 200 & \cite{DOPC1DOPE1berger} \\
  \todo{Data for POPC:POPG mixtures by listed by Antonio Peon is missing from this table} \\

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPG.pdf}
  \caption{\label{HGorderParametersPOPG}
    The headgroup and glycerol backbone order parameters of PG lipids
    from experiments (POPG and signs from this work and from Ref.~\citenum{borle85}, %contains 10mM of PIPES,
    DPPG with 100mM NaCl from Ref.~\citenum{wohlgemuth80},% contains 10mM PIPES and,
    and E.Coli PG results from Ref.~\citenum{gally81}).
    and simulations with different force fields.
  }
\end{figure}
\begin{figure*}[!h]
  \centering
  \includegraphics[width=18.0cm]{../Figs/PCPEPGPSstructures.png}
  \includegraphics[width=8.0cm]{../Figs/PCPEPGPSdihedrals1.png}
  \includegraphics[width=8.0cm]{../Figs/PCPEPGPSdihedrals2.png}
  \caption{\label{structures}
    Overlayed snapshots and dihedral angle distributions from CHARMM36 simulations of different lipids which give the best agreement with experiments.
  }
\end{figure*}

>>>>

      POPE  & OPLS-MacRog \cite{rog16}        &0    & 144	& 5760     &0    & 310  & 500 & 350 & \cite{MacRogPOPEfiles} \\

@@

\begin{table*}[htb]
  %\begin{sidewaystable*}[!p]
  \centering
  \caption{List of MD simulations with PE and PG lipids mixed with PC.
    % The salt concentrations calculated as [salt]=N$_{\rm c} \times$[water]\,/\,N$_{\rm w}$, where [water]\,=\,55.5~M.
    % these correspond the concentrations reported in the experiments by Akutsu et al.~\cite{akutsu81}.
    % The lipid force fields named as in our previous work~\cite{botan15}.
  }\label{systemsMIX}
  \begin{minipage}[t]{\textwidth}
    \begin{tabular}{l c c r r r r r r c c}
      %\hline
      % some footnotes are not visible in typeset-MS (pdf)
      lipid/counter-ions & force field for lipids / ions & NaCl (M) & CaCl$_2$\,(M) &  \footnote{Number of lipid molecules with largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$   & \footnote{Number of additional cations}N$_{\rm c}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns) & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns) &   \footnote{Reference for simulation files}files\\
      \hline
      POPC                   & CHARMM36 \cite{??}        & 0.11      & 0  & 500     & 25000 & 48  &  310  & 500 & 100 & \cite{POPCcharmm150mMNaCl301K}  \\
      POPC:POPG (7:3)        & CHARMM36 \cite{??}        & 0.11      & 0  & 350     & ?     & ?   &  310  & 500 & 100 & \cite{POPC7POPG1charmm36NaCl}  \\
      POPC:POPG (1:1)/K$^+$  & CHARMM36 \cite{??}        &0          & 0  & 250:250 & 18158 & 0   &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG5050} \\ 
      POPC:POPG (1:1)        & CHARMM36 \cite{??}        &0          & 0.34 \todoi{Concentration calculated based in total amount of calcium ions. This may not be reasonable due to the lack of counterions.}  & 250:250 & 20798 & 128 &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG5050150mMCaCl} \\
      POPC:POPG (1:1)        & CHARMM36 \cite{??}        &0          & 1.36  \todoi{Concentration calculated based in total amount of calcium ions. This may not be reasonable due to the lack of counterions.} & 250:250 & 18114 & 445  &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG50501000mMCaCl} \\
      POPC:POPG (4:1)/K$^+$  & CHARMM36 \cite{??}        &0          & 0  & 400:100 & 18664 & 0  &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG4010} \\
      POPC:POPG (4:1)/K$^+$  & CHARMM36 \cite{??}        &0          & 1.0 \todoi{Concentration calculated based in total amount of calcium ions. This may not be reasonable due to the lack of counterions.} & 400:100 & 18647 & 419  &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG40101000mMCaCl} \\
      \hline
      POPC             & CHARMM36 \cite{??}        &0          & 0  & 256 & 8704 & 0  &  300  & 300 & 250 & \cite{POPCcharmm300K} \\
      POPC:POPE (1:1)  & CHARMM36 \cite{??}        &0          & 0  & 128 & 8704 & 0  &  300  & 300 & 250 & \cite{POPC1POPE1charmm36} \\
     \hline
      POPC                   & Slipid \cite{??}        & 0.11      & 0  & 500     & 25000 & 48  &  310  & 500 & 100 & \cite{POPCslipid150mMNaCl301K}  \\
      POPC:POPG (7:3)        & Slipid \cite{??}        & 0         & 0  & 350:150 & 25000 & 0   &  310  & 500 & 100 & \cite{slipidPOPC70POPG30T310K} \\
      POPC:POPG (1:1)        & Slipid \cite{??}        & 0         & 0  & 128:128 & 12800 & 0   &  298  & 500 & 400 & \cite{slipidPOPC50POPG50T298K} \\
      POPC:POPG (1:1)        & Slipid \cite{??}        & 0         & 0.1  & 128:128 & 12800 & 23  &  298  & 500 & 400 & \cite{slipidPOPC50POPG50T298K} \\
      POPC:POPG (1:1)        & Slipid \cite{??}        & 0         & 0.2  & 128:128 & 12800 & 46  &  298  & 1500 & 500 & \cite{slipidPOPC50POPG50T298K} \\
      POPC:POPG (1:1)        & Slipid \cite{??}        & 0         & 0.5  & 128:128 & 12800 & 115 &  298  & 1500 & 500 & \cite{slipidPOPC50POPG50T298K} \\
      POPC:POPG (1:1)        & Slipid \cite{??}        & 0         & 1.0  & 128:128 & 12800 & 230 &  298  & 1500 & 500 & \cite{slipidPOPC50POPG50T298K} \\

      \hline
      POPC:POPG (4:1)        & Lipid17 \cite{??}       &0          & 0  & 350:88 & 26265 & 0  &  298  & 400 & 350 & \cite{Lipid17POPCPOPG8020} \\
      POPC:POPG (4:1)        & Lipid17 \cite{??}       &0          & 0.1& 350:88 & 26124 & 47 &  298  & 400 & 150 & \cite{Lipid17POPCPOPG8020100mMCaCl} \\
      POPC:POPG (4:1)        & Lipid17 \cite{??}       &0          & 1.0& 350:88 & 24840 & 475 &  298  & 1200 & 200 & \cite{Lipid17POPCPOPG80201000mMCaCl} \\
      POPC:POPG (1:1)        & Lipid17 \cite{??}       &0          & 0  & 150:150 & 31572 & 0  &  298  & 320 & 200 & \cite{Lipid17POPCPOPG5050} \\
      POPC:POPG (1:1)        & Lipid17 \cite{??}       &0          & 0.1& 150:150 & 31401 & 57 &  298  & 720 & 198 & \cite{Lipid17POPCPOPG5050100mMCaCl} \\
      POPC:POPG (1:1)        & Lipid17 \cite{??}       &0          & 1.0& 150:150 & 29865 & 569 &  298  & 720 & 200 & \cite{Lipid17POPCPOPG50501000mMCaCl} \\
      \hline
      POPC             & Berger \cite{??} \todoi{This is probable not plain berger, correct force filed should be described.}  &0  & 0  & 256 & 10240 & 0  &  300  & 300 & 200 & \cite{POPCberger300K} \\
      POPC:POPE (1:1)  & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.} &0          & 0  & 128 & 11008 & 0  &  300  & 300 & 200 & \cite{POPC1POPE1berger} \\
      POPC:DOPE (1:1)  & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.}         &0          & 0  & 128 & 10240 & 0  &  300  & 300 & 200 & \cite{POPC1DOPE1berger} \\
     \hline
      DOPC             & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.}         &0          & 0  & 256 & 11008 & 0  &  300  & 300 & 200 & \cite{DOPCberger300K} \\
      DOPC:DOPE (1:1)  & Berger \cite{??}   \todoi{This is probable not plain berger, correct force filed should be described.}        &0          & 0  & 128 & 11008 & 0  &  300  & 300 & 200 & \cite{DOPC1DOPE1berger} \\
    \end{tabular}
  \end{minipage}
  %\end{sidewaystable*}
  \todo{Data for POPC:POPG mixtures by listed by Antonio Peon is missing from this table} \\
    \todo{We need citations for the force fields.}
\end{table*}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPG.pdf}
  \caption{\label{HGorderParametersPOPG}
    The headgroup and glycerol backbone order parameters of PG lipids
    from experiments (POPG and signs from this work and from Ref.~\citenum{borle85}, %contains 10mM of PIPES,
    DPPG with 100mM NaCl from Ref.~\citenum{wohlgemuth80},% contains 10mM PIPES and,
    and E.Coli PG results from Ref.~\citenum{gally81}).
    and simulations with different force fields.
  }
\end{figure}
\begin{figure*}[!h]
  \centering
  \includegraphics[width=18.0cm]{../Figs/PCPEPGPSstructures.png}
  \includegraphics[width=8.0cm]{../Figs/PCPEPGPSdihedrals1.png}
  \includegraphics[width=8.0cm]{../Figs/PCPEPGPSdihedrals2.png}
  \includegraphics[width=8.0cm]{../Figs/HGtilt.png}
  \caption{\label{structures}
    Overlayed snapshots and dihedral angle distributions from CHARMM36 simulations of different lipids which give the best agreement with experiments.
  }
\end{figure*}
